---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# rksfun

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/richardstoeckl/rksfun)](https://github.com/richardstoeckl/rksfun/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/richardstoeckl/rksfun)](https://github.com/richardstoeckl/rksfun/pulls)
<!-- badges: end -->

These are some commonly used functions in my work. I have created this package to make my work easier. I hope you find it useful too.

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install the development version from [GitHub](https://github.com/richardstoeckl/rksfun) with:

```{r 'install_dev', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}
BiocManager::install("richardstoeckl/rksfun")
```

## Citation

Below is the citation output from using `citation('rksfun')` in R. Please
run this yourself to check for any updates on how to cite __rksfun__.

```{r 'citation', eval = requireNamespace('rksfun')}
print(citation("rksfun"), bibtex = TRUE)
```

Please note that the `rksfun` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://richardstoeckl.github.io/rksfun) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


